Incentivizing Exploration with Unbiased History

### 2018-10-19 model.tex
stuff

We study the mult-armed bandit problem in a social learning context,
in which a principal faces a sequence of $T$ myopic agents. There is a
set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is
distributed according to the Bernoulli distribution with an unknown
mean $\mu_a$.\swcomment{do we plan to generalize to real-valued?}  At
each round $t\in [T]$, a new agent $t$ arrives, receives a message
$m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a
reward $r_t\in \{0,1\}$ that is immediately observed by the
principal. Given any sequence of arms $\{a_1, \ldots, a_T\}$ chosen by
the agents, the \emph{regret} is defined as
\[
  \reg(T)= \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a -
  \sum_{t=1}^T \mu_{a_t}.
\]

@@

\xhdr{Unbiased sub-history policy.} The principal's goal is to reveals
a sequence of messages accroding to a disclosure policy so that the
regret of the induced sequence of actions is minimized. We will focus
on \emph{unbiased sub-history policies} that at each round $t$ reveal
the \emph{sub-history} in a subset of previous rounds
$S_t\subseteq [t-1]$: $\{(s, a_s, r_s)\mid s \in S_t\}$, where the
subset $S_t$ is fixed ahead of time. A simple example is the policy
that reveals the \emph{full history}, that is $S_t = [t-1]$.  All of
the policies we develop are \emph{transitive}: for any two agents $t$
and $t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains
that of $S_{t'}$.

@@

\xhdr{Agents' behavior.} Based on the history over rounds $S_t$, each
agent $t$ first computes an estimate $\hat{\mu}_a^t$ for the mean
reward of each arm $a$, and then selects the arm with the highest
$\hat{\mu}_a^t$. Let $t_a$ be the number of times arm $a$ is pulled in
the observed history $S_t$. For any $a$ with $t_a > 0$, we write
$\bar{\mu}_a^t$ as the empirical average of arm $a$ given the history.

% We assume that for sufficiently high $t_a$, the estimate
% $\hat{\mu}_a^t$ is close to the empirical average $\bar{\mu}_a^t$.

We will make the following assumptions on the set of mean rewards
$\{\mu_a\}$, and the relationship between the estimates $\hat \mu_a^t$
.and empirical mean rewards $\bar\mu_a^t$.

\begin{assumption}
\label{ass:embehave}
Let $c_m = 1/16$.\swcomment{subscript $m$ meant anything?}. 
\begin{itemize}
\item The mean reward $\mu_a$ for each arm $a\in \A$ lies in the range
  of $[1/3, 2/3]$.

\item There exists a constant $c_T$ such that for any agent $t$ and
  arm $a$, as long as $t_a \geq c_T$,
\[
  \left|\hat{\mu}^t_a - \bar{\mu}^t_a \right| <
  \frac{c_m}{\sqrt{t_a}}.
\]
\item In the case of $t_a = 0$, the initial estimate $\hat{\mu}^t_a$
  is at least $1/3$.
\end{itemize}
\end{assumption}

@@

We allow different agents to have different behavior models as long as
they satisfy Assumption \ref{ass:embehave}. More specifically, we
assume each agent's behavior model is sampled from an unknown
distribution independently.\swcomment{why independently? can be be
  adversarial?}
\begin{remark}
  how this relates to Bayesian exploration with conjugate
  priors\swcomment{seems to be something nasty}
\end{remark}

>>>>

We study the mult-armed bandit problem in a social learning context,
in which a principal faces a sequence of $T$ myopic agents. There is a
set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is
distributed according to the Bernoulli distribution with an unknown
mean $\mu_a$.% \swcomment{do we plan to generalize to real-valued?}  
% \jmcomment{Probably not. We probably need some weird assumptions to make it work and we may need to change many parts of our proofs. The assumptions will be like: enough variance for anti-concentration and even more stuff for the greedy to has a small chance to work. Probably binary sound more natural and practical. And we should state something like binary should be interpreted as the feedback from the user, i.e. ``like'' or ``dislike''.}
At each round $t\in [T]$, a new agent $t$ arrives, receives a message
$m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a
reward $r_t\in \{0,1\}$ that is immediately observed by the
principal. Given any sequence of arms $\{a_1, \ldots, a_T\}$ chosen by
the agents, the \emph{regret} is defined as
\[
  \reg(T)= \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a -
  \sum_{t=1}^T \mu_{a_t}.
\]

@@

\xhdr{Unbiased sub-history policy.} The principal's goal is to reveals
a sequence of messages accroding to a disclosure policy so that the
regret of the induced sequence of actions is minimized. We will focus
on \emph{unbiased sub-history policies} that at each round $t$ reveal
the \emph{sub-history} $H_t = \{(s, a_s, r_s)\mid s \in S_t\}$, such
that each $S_t\subseteq [t-1]$ is a subset of previous rounds
\emph{fixed ahead of time}. A simple example is the policy that
reveals the \emph{full history} with $S_t = [t-1]$.  All of the
policies we develop are \emph{transitive}: for any two agents $t$ and
$t'$ such that $t'\in S_t$, then the sub-history of $S_t$ contains
that of $S_{t'}$.

@@

\xhdr{Agents' behavior.} We model agents with heterogeneity in their
arm selections. In particular, each agent $t$ has a private estimator
that maps the revealed sub-history $H_t$ to a mean reward estimate
$\hat{\mu}_a^t$ for every arm $a$, and the agent chooses the arm $a_t$
with the highest estimate. The agents' private estimators are drawn
i.i.d.~from some distribution. For any $t\in[T]$ and $a\in \A$, we
write $N_{t, a}$ and $\bar{\mu}_a^t$ to denote the number of pulls of
$a$ and the empirical mean reward of arm $a$ in $H_t$ respectively. If
an arm is not pulled in $H_t$, we will let $\bar{\mu}_a^t = 0$.

% \swcomment{need to assume i.i.d. types}
% We assume that for sufficiently high $t_a$, the estimate
% $\hat{\mu}_a^t$ is close to the empirical average $\bar{\mu}_a^t$.

We will make the following assumptions on the set of mean rewards
$\{\mu_a\}$, and the relationship between the estimates $\hat \mu_a^t$
and empirical mean rewards $\bar\mu_a^t$.

\begin{assumption}
\label{ass:embehave}
Let $c_m = 1/16$.\swcomment{maybe use a better notation} 
% \jmcomment{It means a constant for some assumptions about means but nothing else. Just want to make it different from other constants. Maybe there are better notations.}. 
\begin{itemize}
\item The mean reward $\mu_a$ for each arm $a\in \A$ lies in the range
  of $[1/3, 2/3]$.

\item There exists a constant $c_T$ such that for any agent $t$ and
  arm $a$, as long as $t_a \geq c_T$,
\[
  \left|\hat{\mu}^t_a - \bar{\mu}^t_a \right| <
  \frac{c_m}{\sqrt{N_{t,a}}}.
\]
\item In the case of $N_{t,a} = 0$, the initial estimate
  $\hat{\mu}^t_a$ is at least $1/3$.
\end{itemize}
\end{assumption}

@@

We allow different agents to have different behavior models as long as
they satisfy Assumption \ref{ass:embehave}. More specifically, we
assume each agent's behavior model is sampled from an unknown
distribution independently.
% \swcomment{why independently? can be be
%   adversarial?} \jmcomment{Actually current proofs don't work when it's adversarial. It's fairly annoying for the anti-concentration argument. In the proof, we need to use independent to show that the amount of agents pulling arm $a$ in the first level is concentrated to $T_1 q_a$.}
\begin{remark}
  how this relates to Bayesian exploration with conjugate
  priors\swcomment{seems to be something nasty}
\end{remark}
